Modelling circumstellar discs with 3D radiation hydrodynamics

### 2009-08-26 SPH-Torus-paper1/sphtorus_benchmark.tex
Updated section of SPH-Torus disc.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2025 25464f21-6099-402c-b30a-640f1d40d38b

@@

%%% Up to here so far ... %%%

The surface density of the disc, after 4986~years of simulated time
(the latest simulated time), is shown in Fig.~\ref{fig:sigma_final}.
Away from the inner and outer edges of the disc the surface density is
well represented by a power law profile as a function of radius.
\begin{figure}
  \includegraphics[scale=0.3]{figures/sigma_final}
  \caption{Surface density as a function of radius after 4986~years of simulated time.}
  \label{fig:sigma_final}
\end{figure}

The scale height of the disc was determined by fitting Gaussians to
the vertical density profile in 100 radial bins. The fitted scale
height, as a function of radius, is plotted in
Fig.~\ref{fig:scale_height}.  Within the central 10~AU the density
profile appears flat so it was not possible to fit a meaningful scale
height.
\begin{figure}
  \includegraphics[scale=0.3]{figures/scale_height}
  \caption{Disc scale height as a function of radius  after 4986~years of simulated time.}
  \label{fig:scale_height}
\end{figure}

The average temperature within one scale height of the disc mid plane
is plotted as a solid line in Fig.~\ref{fig:mid_tem}. The dashed line
is a power law variation of temperature with radius with an index of
$-0.35$. Although this line is not a formal best fit it has been
plotted to indicate that this temperature profile is well represented
by a power law outside 15AU.
\begin{figure}
  \includegraphics[scale=0.3]{figures/mid_tem}
  \caption{Average temperature within one scale height of the mid plane, as a function of
    radius, after 4986~years of simulated time.}
  \label{fig:mid_tem}
\end{figure}

>>>>

\subsection{Results}

@@

The surface density of the disc is shown in Fig.~\ref{fig:sigma} where
the solid line is the isothermal disc and the dotted line is the disc
at the final time step.  Away from the inner and outer edges of the
disc the surface density is well represented by a power law profile as
a function of radius.
\begin{figure}
  \includegraphics[scale=0.3]{figures/sigma}
  \caption{Surface density as a function of radius.}
  \label{fig:sigma}
\end{figure}
The scale height of the disc was determined by fitting Gaussians to
the vertical density profile in 100 radial bins. The fitted scale
height, as a function of radius, is plotted in
Fig.~\ref{fig:scale_height}.  Within the central 10~AU the density
profile appears flat so it was not possible to fit a meaningful scale
height. The solid line is the isothermal disc and the dotted line is
the disc at the final time step.
\begin{figure}
  \includegraphics[scale=0.3]{figures/scale_height}
  \caption{Disc scale height as a function of radius.}
  \label{fig:scale_height}
\end{figure}
The average temperature within one scale height of the disc mid plane
is plotted in Fig.~\ref{fig:mid_tem}. The solid line is the isothermal
disc and the dotted line is the disc at the final time step.
\begin{figure}
  \includegraphics[scale=0.3]{figures/mid_tem}
  \caption{Average temperature within one scale height of the mid plane as a function of
    radius.}
  \label{fig:mid_tem}
\end{figure}
